Finding Subgraphs With Side Constraints\thanks{This research was supported by the Engineering and Physical Sciences Research Council [grant number EP/P026842/1]}

### 2021-04-20 paper/paper.tex
Camera ready

\author{
    \"Ozg\"ur Akg\"un\inst{1}\orcidID{0000-0003-4460-6912} \and Jessica
    Enright\inst{2}\orcidID{0000-0002-0266-3292} \and Christopher
    Jefferson\inst{1}\orcidID{0000-0003-2979-5989} \and Ciaran
    McCreesh\inst{2}\orcidID{0000-0002-6106-4871} \and Patrick
    Prosser\inst{3}\orcidID{0000-0003-4460-6912} \and Steffen
    Zschaler\inst{4}\orcidID{0000-0001-9062-6637} \\
}
\authorrunning{\"O. Akg\"un et al.}
\institute{
    University of St Andrews, Scotland \and
    University of Glasgow, Scotland \\ \email{ciaran.mccreesh@glasgow.ac.uk} \and
    Algorithmicists Anonymous, Scotland \and
    King's College London, England
}

@@

\subsection{Preliminary Experiments and Motivation}

Unfortunately, whilst elegant and flexible, the performance of this approach leaves a lot to be
desired on basic subgraph isomorphism instances.  The computational experiments in this paper are
performed on a cluster of machines with dual Intel Xeon E5-2697A v4 processors and 512GBytes RAM
running Ubuntu 18.04.  We will be using the 14,621 unlabelled, undirected instances from
Solnon's benchmark suite\footnote{https://perso.liris.cnrs.fr/christine.solnon/SIP.html}. This
benchmark suite was originally designed for algorithm portfolios work
\cite{DBLP:conf/lion/KotthoffMS16}, and brings together several collections of application and
randomly-generated instances with varying difficulties and solution counts (including many
unsatisfiable instances). Some of the instances have up to 900 vertices and 14,420 edges in patterns
and up to 6,671 vertices and 209,000 edges in targets. These lead to rather large models, by
constraint programming standards: the largest generated table constraint has nearly half a million
entries. However, these sizes are realistic from an applications perspective, and it would be
desirable if solvers could handle even larger target graphs.

>>>>

\author{
    \"Ozg\"ur Akg\"un\inst{1}\orcidID{0000-0003-4460-6912} \and Jessica
    Enright\inst{2}\orcidID{0000-0002-0266-3292} \and Christopher
    Jefferson\inst{1}\orcidID{0000-0003-2979-5989} \and Ciaran
    McCreesh\inst{2}\orcidID{0000-0002-6106-4871} \and Patrick
    Prosser\inst{2}\orcidID{0000-0003-4460-6912} \and Steffen
    Zschaler\inst{3}\orcidID{0000-0001-9062-6637} \\
}
\authorrunning{\"O. Akg\"un et al.}
\institute{
    University of St Andrews, Scotland \and
    University of Glasgow, Scotland \\ \email{ciaran.mccreesh@glasgow.ac.uk} \and
    King's College London, England
}

@@

\subsection{Initial Experiments and Motivation}

Unfortunately, whilst elegant and flexible, the performance of this approach leaves a lot to be
desired on basic subgraph isomorphism instances.  The computational experiments in this paper are
performed on a cluster of machines with dual Intel Xeon E5-2697A v4 processors and 512GBytes RAM
running Ubuntu 18.04. The source code used for these experiments is released as part of the Glasgow
Subgraph
Solver\footnote{\url{https://github.com/ciaranm/glasgow-subgraph-solver/releases/tag/cpaior2021-finding-subgraphs-with-side-constraints}},
Minion\footnote{\url{https://github.com/minion/minion/releases/tag/1.9}}, and
Conjure\footnote{\url{https://github.com/conjure-cp/conjure}} distributions.

For graphs, we will be using the 14,621 unlabelled, undirected instances from
Solnon's benchmark suite\footnote{\url{https://perso.liris.cnrs.fr/christine.solnon/SIP.html}}. This
benchmark suite was originally designed for algorithm portfolios work
\cite{DBLP:conf/lion/KotthoffMS16}, and brings together several collections of application and
randomly-generated instances with varying difficulties and solution counts (including many
unsatisfiable instances). Some of the instances have up to 900 vertices and 14,420 edges in patterns
and up to 6,671 vertices and 209,000 edges in targets. These lead to rather large models, by
constraint programming standards: the largest generated table constraint has nearly half a million
entries. However, these sizes are realistic from an applications perspective, and it would be
desirable if solvers could handle even larger target graphs.
